---
title: "Simulating gun vs thing"
author: "Solveig Lindberg"
date: "`r Sys.Date()`"
output: pdf_document
---

alright time to simulate gun vs warhammer things (default "marine with 5++")
N is amount of sims, default 40k (this usually means you get things right within a percentage point or so, no formal guarantees are given)
Insert Stats:
```{r}
N <- 40000
FlatA <- 4
RandomAttacks = FALSE
VariableA <- c(2,6) #("xdy", eg: Flamer would be (1,6) for 1d6.)

#remaining: code sustained hits
SustainedHits= FALSE
SustainedHitsValue = 0
LethalHits = FALSE
DevastatingWounds = FALSE
Torrent = FALSE
#weapon stats
BS <- 2
S <- 18
Ap <- -4+1 #Add 1 if cover applies
FlatD <- 6
RandomDamage <- FALSE
VariableD <- c(1,6) #("xdy", eg: Brightlance would be (1,6) for 1d6.)

WoundModifier <- 1 #(0, 1 or -1)

#Target defensive characteristics
ModelWounds <- c(18)
Toughness <- 12
SV <- 2
Invuln <- 4 #set number to the book value - if unit has no Invulnerable Save, set it larger than six.
FNP <- 20 #set number to the book value - if unit has no FNP, set it larger than six.

#Toughness calcs:
if(S<Toughness){ToughtoBeat <- 5}
if(S==Toughness){ToughtoBeat <- 4}
if(S>Toughness){ToughtoBeat <- 3}
if((S/2)>=Toughness){ToughtoBeat <- 2}
if((S*2)<=Toughness){ToughtoBeat <- 6}


#maybe eventually deal with cover, but like, later. very low down on the priority list.
#normal rerolls, no weird
reRollAllHits = FALSE
reRoll1Hits = FALSE
reRollAHit = TRUE
reRollAllWounds = FALSE
reRoll1Wounds = FALSE
reRollAWound =TRUE
#implement six-fishing later, but don't expect to end up in such worlds often
AdditiveDamageModifier= 0
MultiplicativeDamageModifier=1
```

Count the fucking modifier to hit your own godsdamned self btw, I Ain't Doing It.
Also Invulns are sacred shut the fuck up

Attack Calcs:
```{r}
if(RandomAttacks==TRUE){
  TotalA <- numeric(N*(FlatA+(VariableA[1]*VariableA[2])))
  dim(TotalA)<-cbind(c(N,FlatA+(VariableA[1]*VariableA[2])))
  for (i in 1:N){
    AttackRoll <- sum(sample.int(VariableA[2],VariableA[1], replace = TRUE))
    for(j in 1:(FlatA+(VariableA[1]*VariableA[2]))){
      if((FlatA+AttackRoll)>=j){
        TotalA[i,j] <- 1
      }else{
        TotalA[i,j] <- 0
      }
    }
  }
}
```


Hit calcs:
```{r}
if(RandomAttacks==FALSE){
  Hitrolls <- sample.int(6, FlatA*N , replace=TRUE)
  dim(Hitrolls)<-cbind(c(N,FlatA))
}else{
  Hitrolls <- numeric(N*(FlatA+(VariableA[1]*VariableA[2])))
  dim(Hitrolls) <- cbind(c(N,FlatA+(VariableA[1]*VariableA[2])))
  for (i in 1:N){
    for(j in 1:(FlatA+(VariableA[1]*VariableA[2]))){
      if(TotalA[i,j]==1){
        Hitrolls[i,j] <- sample.int(6,1,replace=TRUE)
      }
    }
  }
}  
NormalHits <- Hitrolls>= BS
if(Torrent==TRUE){
  NormalHits <- Hitrolls>0
}
CriticalHits <- Hitrolls==6
Failedhits <- 1-NormalHits
NNormalHits <- as.numeric(NormalHits)

if(RandomAttacks==FALSE){
  dim(NNormalHits) <- cbind(c(N,FlatA))
}else{
  dim(NNormalHits) <- cbind(c(N,(FlatA+(VariableA[1]*VariableA[2]))))
}

#add re-rolls here, but not now

#TotalHits <- rowSums(NormalHits+CriticalHits*SustainedHitsValue)
```



Wound calcs:
```{r}
if(RandomAttacks==FALSE){
  Woundrolls <- numeric(FlatA*N) 
  dim(Woundrolls)<-cbind(c(N,FlatA))
  for (i in 1:N){
    for(j in 1:FlatA){
      if(NNormalHits[i,j]==1){
        Woundrolls[i, j] <-sample(c(1:6), 1, replace=TRUE)
      } else {
       Woundrolls[i, j] <- 0
      }
    }
  }
  NormalWounds <- ((Woundrolls>=ToughtoBeat-(WoundModifier)))

  if(LethalHits==TRUE){
    NormalWounds = 0>(NNormalWounds+CriticalHits)
    NNormalWounds <- as.numeric(NormalWounds)
    dim(NNormalWounds)<-cbind(c(N,FlatA))
  }else{
    NNormalWounds <- as.numeric(NormalWounds)
    dim(NNormalWounds)<-cbind(c(N,FlatA))
  }
}else{
  Woundrolls <- numeric(N*(FlatA+(VariableA[1]*VariableA[2])))
  dim(Woundrolls)<-cbind(c(N,FlatA+(VariableA[1]*VariableA[2])))
  for (i in 1:N){
    for(j in 1:(FlatA+(VariableA[1]*VariableA[2]))){
      if(NNormalHits[i,j]==1){
        Woundrolls[i, j] <-sample(c(1:6), 1, replace=TRUE)
      } else {
       Woundrolls[i, j] <- 0
      }
    }
  }
  NormalWounds <- (Woundrolls>=(ToughtoBeat-(WoundModifier)))

  if(LethalHits==TRUE){
    NormalWounds = 0>(NNormalWounds+CriticalHits)
    NNormalWounds <- as.numeric(NormalWounds)
    dim(NNormalWounds)<-cbind(c(N,(FlatA+(VariableA[1]*VariableA[2]))))
  }else{
    NNormalWounds <- as.numeric(NormalWounds)
    dim(NNormalWounds)<-cbind(c(N,(FlatA+(VariableA[1]*VariableA[2]))))
  }
}


 CriticalWounds <- (Woundrolls==6)
  if(DevastatingWounds==TRUE&&LethalHits==TRUE){
    CriticalWounds=CriticalWounds-CriticalHits
  }
  #devastating wounds?
  if(DevastatingWounds==TRUE){
    NNormalWounds <- NNormalWounds-CriticalWounds
  }
```

```{r}
dim(NNormalWounds)
```


Save calcs:
```{r}
Saverolls <- numeric(dim(NNormalWounds)[2]*N) #Use ((SustainedHitsValue+1)*FlatA*N) everywhere when implementing sustained hits
dim(Saverolls)<-cbind(c(N,dim(NNormalWounds)[2]))

for (i in 1:N){
  for(j in 1:dim(NNormalWounds)[2]){
    if(NNormalWounds[i,j]==1){
    Saverolls[i, j] <-sample.int(6, 1, replace=TRUE)
    } else {
    Saverolls[i, j] <- 20
    }
  }
}
FailedSaves <- Saverolls<=min((SV-Ap),Invuln)
NFailedSaves <- as.numeric(FailedSaves)
dim(NFailedSaves) <- cbind(c(N,dim(NNormalWounds)[2]))
```
Resulting Total Damage Calcs:
```{r}
DamageApplications <- rowSums(NFailedSaves)
TotalDamage <- numeric(N)
if (RandomDamage==FALSE){
  TotalDamage <- FlatD*DamageApplications
} else {
  for (i in 1:N){
    for (j in 1:DamageApplications[i]){
      Drolls <- sample.int(VariableD[2],VariableD[1],replace=TRUE)+FlatD
      TotalDamage[i] <- +Drolls
    }
  }
}
```
Resulting Model destruction Calcs:
```{r}
SimDamageApplications <- DamageApplications

SimModels <- numeric(N*length(ModelWounds))
SimModels <- rep(ModelWounds, N)
dim(SimModels)<-(cbind(c(N,length(ModelWounds))))
for(i in 1:N){
  jstar <- 1
  while ((SimDamageApplications[i]>0)&&(SimModels[i,length(ModelWounds)]>0)) {
    if(SimModels[i,jstar]<=0){
      jstar = jstar+1
    }
    SimModels[i,jstar] <- SimModels[i,jstar] -max((MultiplicativeDamageModifier*(FlatD+(as.numeric(RandomDamage)*sum(sample.int(VariableD[2],VariableD[1],replace=TRUE))))+AdditiveDamageModifier),1)
    SimDamageApplications[i] = SimDamageApplications[i]-1
  }
}
if(DevastatingWounds==TRUE){
  TotalMortals <- 0
  DevWoundsApplications <- rowSums(CriticalWounds)
  RemainingDevWoundsApplications <- DevWoundsApplications
  for(i in 1:N){
    while(RemainingDevWoundsApplications[i]>0){
      TotalMortals <- TotalMortals+max((MultiplicativeDamageModifier*(FlatD+(as.numeric(RandomDamage)*sum(sample.int(VariableD[2],VariableD[1],replace=TRUE))))+AdditiveDamageModifier),1)
      RemainingDevWoundsApplications[i] <- RemainingDevWoundsApplications[i]-1
    }
    jstar <- 1
    while((TotalMortals>0)&&(SimModels[i,length(ModelWounds)]>0)){
      while(SimModels[i,jstar]<=0){
        jstar = jstar+1
      }
      SimModels[i, jstar] = SimModels[i, jstar]-1
      TotalMortals = TotalMortals-1
    }
  }
}

SurvivingModels <- rowSums(SimModels>0)
```


Data Analysis and graphs and shit
```{r}
DestroyedModels <- length(ModelWounds)-SurvivingModels

hist(TotalDamage)
plot.ecdf(SurvivingModels) #probability of this many models or fewer remaining
plot.ecdf(DestroyedModels) #probability of this many models or fewer destroyed

```

```{r}
TableTotalDamage <- table(TotalDamage)
TableTotalDamage/N
1-cumsum(TableTotalDamage/N)+TableTotalDamage/N
TableDestroyedModels <- table(DestroyedModels)
TableDestroyedModels/N
1-cumsum(TableDestroyedModels/N)+TableDestroyedModels/N #probability estimate of X models destroy or more
```
