---
title: "Rolling."
author: "Solveig Lindberg"
date: "`r Sys.Date()`"
output: pdf_document
---

Computing only expected values in this doc

Equations!! Against Light Marines, though with 5++ invulns - representing the defensive tricks one might run into.
```{r}
#biting blade
bbwoundsdealt <- 1
bbdmg <- 2*bbwoundsdealt
bbM <- bbdmg
bbs <- (3/6)*bbdmg
#no rerolls
bbWnoRe <- (1/6)*bbM +(3/6)*bbs
bbHnoRe <-(4/6)*bbWnoRe+(1/6)*2*bbWnoRe
#rerolls
bbWRe <- (1/6)*bbM+(3/6)*bbs+(2/6)*bbWnoRe
bbHRe <- (4/6)*bbWRe+(1/6)*2*bbWRe
#Fishing for sixes:
bbWsixRe <-(1/6)*bbM+(5/6)*bbWnoRe
bbHsixRe <-(4/6)*bbWsixRe+(1/6)*2*bbWsixRe

#scorpion chainsword
scdmg <- 1
scM <- scdmg
scs <- (2/6)*scdmg
#no rerolls
scWnoRe <- (1/6)*bbM+(2/6)*scs
scHnoRe <- (4/6)*scWnoRe+(1/6)*2*scWnoRe
#rerolls
scWRe <- (1/6)*scM+(2/6)*scs+(3/6)*scWnoRe
scHRe <- (4/6)*scWRe+(1/6)*2*scWRe
#Fishing for sixes:
scWsixRe <-(1/6)*scM+(5/6)*scWnoRe
scHsixRe <-(4/6)*scWsixRe+(1/6)*2*scWsixRe

#Ahra's Bane
ABwoundsdealt <- 1
ABdmg <- 2*ABwoundsdealt
ABM <- ABdmg
ArBs <- (4/6)*ABdmg
#no rerolls
ABWnoRe <- (1/6)*ABM+(4/6)*ArBs
ABHnoRe <- (2/6)*ABWnoRe+(3/6)*2*ABWnoRe
#rerolls
ABWRe <- (1/6)*ABM+(4/6)*ArBs+(1/6)*ABWnoRe
ABHRe <- (2/6)*ABWRe+(3/6)*2*ABWRe
#fishing
ABWsixRe <- (1/6)*ABM+(5/6)*ABWnoRe
ABHsixRe <- (2/6)*ABWsixRe+(3/6)*2*ABWsixRe
#Isirmathil
Isirwoundsdealt <- 1
Isirdmg <- 1*Isirwoundsdealt
IsirM <- Isirdmg
Isirs <- (3/6)*Isirdmg
#no rerolls
IsirWnoRe <- (1/6)*IsirM+(3/6)*Isirs
IsirHnoRe <- (2/6)*IsirWnoRe+(3/6)*2*IsirWnoRe
#rerolls
IsirWRe <- (1/6)*IsirM+(3/6)*Isirs+(2/6)*IsirWnoRe
IsirHRe <- (2/6)*IsirWRe+(3/6)*2*IsirWRe
#fishing
IsirWsixRe <- (1/6)*IsirM+(5/6)*IsirWnoRe
IsirHsixRe <- (2/6)*IsirWsixRe+(3/6)*2*IsirWsixRe
```

Questions asked:
When rerolling, how should you reroll?
```{r}
5*bbHRe
5*bbHsixRe
5*scHRe
5*scHsixRe
```
10 man unit without re-rolls or 5 man unit with re-rolls? (killing marines and lighter)
```{r}
5*bbHnoRe+(9*4)*scHnoRe
5*bbHRe+(4*4)*scHsixRe
```
Better to have big unit, actually

How to reroll Karandras:
```{r}
5*ABHRe
5*ABHsixRe
5*ABHnoRe
8*IsirHRe
8*IsirHsixRe
8*IsirHnoRe
```
With Karandras, do re-rolls good?
```{r}
5*bbHnoRe+(9*4)*scHnoRe+5*ABHnoRe
5*bbHRe+(4*4)*scHsixRe+5*ABHRe
20.16667-14.14815
28.31481-23.65432
```
still better with more, but gap slightly closer.
The smaller unit kills 10-blocks of marines in expectation, would have to do sims to know better. Probably good enough, especially with the utility of extra Falcon/you like it. God this man slaps hard though

against terminators:
```{r}
#biting blade
bbwoundsdealt <- 1
bbdmg <- 2*bbwoundsdealt
bbM <- bbdmg
bbs <- (2/6)*bbdmg
#no rerolls
bbWnoRe <- (1/6)*bbM +(2/6)*bbs
bbHnoRe <-(4/6)*bbWnoRe+(1/6)*2*bbWnoRe
#rerolls
bbWRe <- (1/6)*bbM+(2/6)*bbs+(3/6)*bbWnoRe
bbHRe <- (4/6)*bbWRe+(1/6)*2*bbWRe
#Fishing for sixes:
bbWsixRe <-(1/6)*bbM+(5/6)*bbWnoRe
bbHsixRe <-(4/6)*bbWsixRe+(1/6)*2*bbWsixRe

#scorpion chainsword
scdmg <- 1
scM <- scdmg
scs <- (1/6)*scdmg
#no rerolls
scWnoRe <- (1/6)*bbM+(1/6)*scs
scHnoRe <- (4/6)*scWnoRe+(1/6)*2*scWnoRe
#rerolls
scWRe <- (1/6)*scM+(1/6)*scs+(4/6)*scWnoRe
scHRe <- (4/6)*scWRe+(1/6)*2*scWRe
#Fishing for sixes:
scWsixRe <-(1/6)*scM+(5/6)*scWnoRe
scHsixRe <-(4/6)*scWsixRe+(1/6)*2*scWsixRe

#Ahra's Bane
ABwoundsdealt <- 1
ABdmg <- 2*ABwoundsdealt
ABM <- ABdmg
ArBs <- (3/6)*ABdmg
#no rerolls
ABWnoRe <- (1/6)*ABM+(3/6)*ArBs
ABHnoRe <- (2/6)*ABWnoRe+(3/6)*2*ABWnoRe
#rerolls
ABWRe <- (1/6)*ABM+(3/6)*ArBs+(2/6)*ABWnoRe
ABHRe <- (2/6)*ABWRe+(3/6)*2*ABWRe
#fishing
ABWsixRe <- (1/6)*ABM+(5/6)*ABWnoRe
ABHsixRe <- (2/6)*ABWsixRe+(3/6)*2*ABWsixRe
#Isirmathil
Isirwoundsdealt <- 1
Isirdmg <- 1*Isirwoundsdealt
IsirM <- Isirdmg
Isirs <- (2/6)*Isirdmg
#no rerolls
IsirWnoRe <- (1/6)*IsirM+(3/6)*Isirs
IsirHnoRe <- (2/6)*IsirWnoRe+(3/6)*2*IsirWnoRe
#rerolls
IsirWRe <- (1/6)*IsirM+(3/6)*Isirs+(2/6)*IsirWnoRe
IsirHRe <- (2/6)*IsirWRe+(3/6)*2*IsirWRe
#fishing
IsirWsixRe <- (1/6)*IsirM+(5/6)*IsirWnoRe
IsirHsixRe <- (2/6)*IsirWsixRe+(3/6)*2*IsirWsixRe
```

Terminators and other heavy infantry (sorta)
```{r}
5*bbHRe
5*bbHsixRe
5*scHRe
5*scHsixRe
```
10 man unit without re-rolls or 5 man unit with re-rolls? (killing marines and lighter)
```{r}
5*bbHnoRe+(9*4)*scHnoRe
5*bbHRe+(4*4)*scHsixRe
(4*4)*scHsixRe
```

How to reroll Karandras:
```{r}
5*ABHRe
5*ABHsixRe
5*ABHnoRe
8*IsirHRe
8*IsirHsixRe
8*IsirHnoRe
```

```{r}
5*bbHnoRe+(9*4)*scHnoRe+5*ABHnoRe
5*bbHRe+(4*4)*scHsixRe+5*ABHRe
15.77778-11.64815
21.33333-19.05556
```

Against tougher targets (you don't wanna charge those unless you can brutalise them, you won't live to regret it. Though you do actually deal good dmg, not accounting for the issues of breakpoints in damage types. You lose out on raw dmg but it might be worth using Isirmathil just for the reliability of D1 not being reduced by Terminator models having 3 wounds. Though tbh it looks like it's always better to take the big profile against termies, unless they start at one wound possibly.) the re-rolls get much better than the raw volume (surprising!!). 

You expect to kill about 6 terminators with the Striking Scorpions so they are in fact a legitimate midboard missile threat (they will not survive this but if you kill 200+ pts of termies for your investment of 175 pts of striking scorpions you're still actually efficient, especiallly if this gives you VP and can maybe save the scorpions)